### 2023-01-10 extension.rmd
some small edits

One might argue our seed dictionaries are not validated. We deem that the criterion validity of our dictionary should be built-in. Coverage of China, by definition, should mention words about China. We also maintain that it is difficult to conduct a human validation of the seed dictionaries because the useNews dataset [@puschmann:2020] doesn’t provide access to the full-length articles. Nonetheless, we attempted to conduct such validation by randomly selecting 10 matching and 10 non-matching items for each language. In total, 160 items were selected. A coder with no knowledge of the ground truth (matching or not) annotated the full-text articles by following the URLs in the meta data provided in the useNews dataset [@puschmann:2020]. For some languages, the coder used Google Translate to translate the full text article to English. In total, only 138 URLs were still accessible. Comparing the ground truth and the human coding, 62 and 70 are true-positive and true-negative cases. There are also 5 false-negative and 1 false-positive cases. There are several reasons not related to our seed dictionaries that could lead to the 6 misclassified cases. The false-positive case is Korean and that could be due to incorrect tokenization at the Media Cloud’s end. The 5 false-negative cases are in Norwegian, Portuguese, and Romanian. The content on the website might have changed since Media Cloud collected the data. For example, the ever-changing content in the sidebar might be counted as “main content” and recorded in the DTM. Despite all these caveats, our seed dictionaries have a precision and recall of 98.4% and 92.5% respectively. For the purpose of demonstrating regression analysis, this level of accuracy is more than sufficient.

@@

[^POWER]: Statistical power is a frequentist concept specifying the long run probability of correctly rejecting the null hypothesis. It is usually not relevant for Bayesian inference.

@@

The proportion of 95\% HDI falling inside the ROPE is 0\%. Figure \@ref(fig:figrope) also displays that the 95\% HDI (the pink region) have no overlap with the ROPE (the shaded region). Using the decision rules by @kruschke:2018:RAP, there are 3 possible scenarios: reject the null (when most of the 95\% HDI falls outside the ROPE), accept the null (when most of the 95\% HDI falls inside the ROPE) and undecided (when it can’t be decided). In the current situation, it is very clear that the 95\% HDI falls outside of the ROPE as there is 0\% overlap. Similar to the result from *hypothesis()*, there is a practical effect and it is correct to reject the null hypothesis.

@@

In this situation, the proportion of 95\% HDI falls inside the ROPE is 68\%. The proportion is quite high but it is not decisive. @kruschke:2018:RAP suggests accepting the null when more than 95\% of the 95\% HDI falls inside the ROPE. Accordingly, the current situation of 68\% is "undecided". It might be worthwhile to retest the hypothesis with a larger amount of data.

One should note that the decision rules by @kruschke:2018:RAP depend on many methodological decisions, e.g. how to determine the ROPE, how wide should the ROPE be, and which level of HDI to use. ROPE is also sensitive to the scale of measurement. Nonetheless, ROPE can provide much richer information to inform how future studies should be designed.

@@

# Leave-one-out cross validation of Example 2

Another way to compare the cubic model and the parsimonious model is to conduct a leave-one-out cross validation (LOO). The basic idea of LOO is to study the out-of-sample accuracy of the model by removing one data point at a time. Given the rest of the data and the prediction model, one evaluates how accurate is the model to predict the outcome of the removed data point. The Bayesian LOO estimate of out-of-sample predictive fit ($elpd_{loo}$) can be used to compare the out-of-sample accuracy of models [@vehtari:2016:PBW].

In R, the LOO cross validation of the two models (parsimonious model: *ppa_mod*; cubic model *ppa_qmod*) can be launched with the function `loo`.

@@

However, the PPCs reveal a property of the Poisson model. Compared with the PPCs of the negative binomial model (the same as Figure 4 in the main text), the Poisson model tends to produce stimulated data with an unusual high level of certainty (both models were based on 61 data points). It is an indication of shrinkage (reduction of standard error, i.e. more false positives) due to overdispersion [the variance of the data is higher than the expectation of the model, see @gardner:1995:R]. Poisson model assumes the data to have only one parameter ($\lambda$), which represents both mean and variance. The current data clearly violates this assumption (the variance is far larger than the mean).

>>>>

One might argue our seed dictionaries are not validated. We deem that the criterion validity of our dictionary should be built-in. Coverage of China, by definition, should mention words about China. We also maintain that it is difficult to conduct a human validation of the seed dictionaries because the useNews dataset [@puschmann:2020] doesn’t provide access to the full-length articles. Nonetheless, we attempted to conduct such validation by randomly selecting 10 matching and 10 non-matching items for each language. In total, 160 items were selected. A coder with no knowledge of the ground truth (matching or not) annotated the full-text articles by following the URLs in the metadata provided in the useNews dataset [@puschmann:2020]. For some languages, the coder used Google Translate to translate the full-text article to English. In total, only 138 URLs were still accessible. Comparing the ground truth and the human coding, 62 and 70 are true-positive and true-negative cases. There are also 5 false-negative and 1 false-positive cases. There are several reasons not related to our seed dictionaries that could lead to the 6 misclassified cases. The false-positive case is Korean and that could be due to incorrect tokenization at the Media Cloud’s end. The 5 false-negative cases are in Norwegian, Portuguese, and Romanian. The content on the website might have changed since Media Cloud collected the data. For example, the ever-changing content in the sidebar might be counted as “main content” and recorded in the DTM. Despite all these caveats, our seed dictionaries have a precision and recall of 98.4% and 92.5% respectively. For the purpose of demonstrating regression analysis, this level of accuracy is more than sufficient.

@@

[^POWER]: Statistical power is a frequentist concept specifying the long-run probability of correctly rejecting the null hypothesis. It is usually not relevant for Bayesian inference.

@@

The proportion of 95\% HDI falling inside the ROPE is 0\%. Figure \@ref(fig:figrope) also displays that the 95\% HDI (the pink region) has no overlap with the ROPE (the shaded region). Using the decision rules by @kruschke:2018:RAP, there are 3 possible scenarios: reject the null (when most of the 95\% HDI falls outside the ROPE), accept the null (when most of the 95\% HDI falls inside the ROPE) and undecided (when it can’t be decided). In the current situation, it is very clear that the 95\% HDI falls outside of the ROPE as there is 0\% overlap. Similar to the result from *hypothesis()*, there is a practical effect and it is correct to reject the null hypothesis.

@@

In this situation, the proportion of 95\% HDI falls inside the ROPE is 68\%. The proportion is quite high, but it is not decisive. @kruschke:2018:RAP suggests accepting the null when more than 95\% of the 95\% HDI falls inside the ROPE. Accordingly, the current situation of 68\% is "undecided". It might be worthwhile to retest the hypothesis with a larger amount of data.

One should note that the decision rules by @kruschke:2018:RAP depend on many methodological decisions, e.g. how to determine the ROPE, how wide the ROPE should be, and which level of HDI to use. ROPE is also sensitive to the scale of measurement. Nonetheless, ROPE can provide much richer information to inform how future studies should be designed.

@@

# Leave-one-out cross-validation of Example 2

Another way to compare the cubic model and the parsimonious model is to conduct a leave-one-out cross-validation (LOO). The basic idea of LOO is to study the out-of-sample accuracy of the model by removing one data point at a time. Given the rest of the data and the prediction model, one evaluates how accurate the model is in predicting the outcome of the removed data point. The Bayesian LOO estimate of out-of-sample predictive fit ($elpd_{loo}$) can be used to compare the out-of-sample accuracy of models [@vehtari:2016:PBW].

In R, the LOO cross-validation of the two models (parsimonious model: *ppa_mod*; cubic model *ppa_qmod*) can be launched with the function `loo`.

@@

However, the PPCs reveal a property of the Poisson model. Compared with the PPCs of the negative binomial model (the same as Figure 4 in the main text), the Poisson model tends to produce stimulated data with an unusual high level of certainty (both models were based on 61 data points). It is an indication of shrinkage (reduction of standard error, i.e. more false positives) due to overdispersion [the variance of the data is higher than the expectation of the model, see @gardner:1995:R]. The Poisson model assumes the data to have only one parameter ($\lambda$), which represents both mean and variance. The current data clearly violates this assumption (the variance is far larger than the mean).
